---
title: "p8105_HW1"
output: html_document
date: "2024-09-14"
---

## P8105 HW1

```{r, echo = FALSE, message= FALSE}
### Package setup, not included in Rmd file
library(ggplot2)
library(dplyr)
```


### Problem 1

```{r}
### Import dataset
data("penguins", package = "palmerpenguins")
### Descriptive analysis
num_var = ncol(penguins)
num_row = nrow(penguins)
print(paste("There are", num_var, "columns and", num_row, "rows in this dataset."))
flipper_length = penguins %>% pull(flipper_length_mm)
mean_FL = mean(na.omit(flipper_length))
print(paste("The mean flipper length of the penguins is", round(mean_FL, 2), "mm."))

```

Description:
There are 8 variables in total in this dataset.
- Species: Qualitative with 3 levels: Adelie, Chinstrap, Gentoo; the specific species of the penguin. 
- Island: Qualitative with 3 levels: Biscoe, Dream, Torgersen; the island the penguin lives.
- bill_length_mm: Quantitative, length of the penguin's bill in mm
- bill_depth_mm: Quantitative, depth of the penguin's bill in mm
- flipper_length_mm: Quantitative, length of the penguin's flipper in mm
- body_mass_g: Quantitative, weight of the penguin in gram
- sex: Qualitative with 2 levels: male, female; sex of the penguin
- year: Quantitative ordinal variable.
Size of the dataset:
- There are 8 columns and 344 rows in this dataset.
Mean flipper length:
The mean flipper length of the penguins is 200.92 mm.



### Problem 2

```{r}

```


