---
title: "p8105_HW1"
output: github_document
date: "2024-09-14"   
author: "Leyang Rui"   
---

## P8105 HW1

```{r, echo = FALSE, message= FALSE}
### Package setup, not included in Rmd file
library(ggplot2)
library(dplyr)
```


### Problem 1

```{r}
### Import dataset
data("penguins", package = "palmerpenguins")
```

Description:  
There are `r ncol(penguins)` variables in total in this dataset.  
- species: Qualitative with `r nlevels(penguins %>% pull(species))` levels: Adelie, Chinstrap, Gentoo; the specific species of the penguin.   
- island: Qualitative with `r nlevels(penguins %>% pull(island))` levels: Biscoe, Dream, Torgersen; the island the penguin lives.  
- bill_length_mm: Quantitative, length of the penguin's bill in mm.   
- bill_depth_mm: Quantitative, depth of the penguin's bill in mm.   
- flipper_length_mm: Quantitative, length of the penguin's flipper in mm.   
- body_mass_g: Quantitative, weight of the penguin in gram.   
- sex: Qualitative with `r nlevels(penguins %>% pull(sex))` levels: male, female; sex of the penguin.   
- year: Quantitative ordinal variable.  

Size of the dataset:
There are `r ncol(penguins)` columns and `r nrow(penguins)` rows in this dataset.

Mean flipper length:
The mean flipper length of the penguins is `r mean(na.omit(penguins %>% pull(flipper_length_mm)))` mm.

```{r, warning=FALSE}
### Scatterplot
species = penguins %>% pull(species)
plot_df =
  tibble(
    x = penguins %>% pull(bill_length_mm),
    y = penguins %>% pull(flipper_length_mm)
  )
bill_flipper_scatter = ggplot(plot_df, aes(x = x, y = y, color = species)) +
  geom_point()
bill_flipper_scatter
```
```{r, message=FALSE, warning=FALSE}
### export plot
ggsave("bill_flipper_scatter.png", plot = bill_flipper_scatter)
```


### Problem 2

```{r, warning=FALSE}
### create dataframe
prob2_df = 
  tibble(
    rand_x = rnorm(10),
    vec_logic = rand_x > 0,
    vec_char = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
    vec_fac = factor(c("august", "august", "august", "setp", "setp", "setp", "setp", "oct", "oct", "oct"))
  )
### compute mean
mean_x = mean(prob2_df %>% pull(rand_x))
mean_logic = mean(prob2_df %>% pull(vec_logic))
mean_char = mean(prob2_df %>% pull(vec_char))
mean_fac = mean(prob2_df %>% pull(vec_fac))
mean_x
mean_logic
mean_char
mean_fac
```

As the code output shows, the means for the random sample of normal distribution and the logical vector work, but the means for the character vector and the factor vector do not.

```{r, results="hide", warning=FALSE}
### convert variables
as.numeric(prob2_df %>% pull(vec_logic))
as.numeric(prob2_df %>% pull(vec_char))
as.numeric(prob2_df %>% pull(vec_fac))
```

As the code output shows, the as.numeric function can successfully turn the logical and the factor variables into numbers, but not the character variable, which it returns NAs. Moreover, for the factor variable, the numbers the function returns are actually the number codes of the factor's levels. So the as.numeric function also cannot turn the factor variable into computable numbers. This explains why we cannot take the means for neither the character nor the factor variables.











