---
title: "p8105_HW1"
output: github_document
date: "2024-09-14"
---

## P8105 HW1

```{r, echo = FALSE, message= FALSE}
### Package setup, not included in Rmd file
library(ggplot2)
library(dplyr)
```


### Problem 1

```{r}
### Import dataset
data("penguins", package = "palmerpenguins")

```

Description:  
There are `r ncol(penguins)` variables in total in this dataset.  
- species: Qualitative with `r nlevels(penguins %>% pull(species))` levels: Adelie, Chinstrap, Gentoo; the specific species of the penguin.   
- island: Qualitative with `r nlevels(penguins %>% pull(island))` levels: Biscoe, Dream, Torgersen; the island the penguin lives.  
- bill_length_mm: Quantitative, length of the penguin's bill in mm.   
- bill_depth_mm: Quantitative, depth of the penguin's bill in mm.   
- flipper_length_mm: Quantitative, length of the penguin's flipper in mm.   
- body_mass_g: Quantitative, weight of the penguin in gram.   
- sex: Qualitative with `r nlevels(penguins %>% pull(sex))` levels: male, female; sex of the penguin.   
- year: Quantitative ordinal variable.  

Size of the dataset:  
- There are `r ncol(penguins)` columns and `r nrow(penguins)` rows in this dataset.

Mean flipper length:
The mean flipper length of the penguins is `r mean(na.omit(penguins %>% pull(flipper_length_mm)))` mm.

```{r}
### Scatterplot
species = penguins %>% pull(species)
plot_df =
  tibble(
    x = penguins %>% pull(bill_length_mm),
    y = penguins %>% pull(flipper_length_mm)
  )
ggplot(plot_df, aes(x = x, y = y, color = species)) +
  geom_point()
```

Make a scatterplot of flipper_length_mm (y) vs bill_length_mm (x); color points using the species variable (adding color = ... inside of aes in your ggplot code should help)

### Problem 2

```{r}

```


